PID Controller Implementation in CARLA Simulator

### 2024-12-02 Article.tex
Update Article.tex

@@

>>>>

% Add the initialization parameters
The PID controller for throttle response was initialized with the following parameters:

\begin{equation}
K_p = 1.0,\quad K_i = 0.1,\quad K_d = 0.0
\end{equation}

These parameters were chosen to provide a strong proportional response for immediate error correction and a small integral action to eliminate steady-state errors. The derivative term was set to zero to avoid amplifying measurement noise and because the system's dynamics did not require derivative control.

@@

The PID controller for steering response was initialized with the following parameters:

\begin{equation}
K_p = 0.5,\quad K_i = 0.0,\quad K_d = 0.1
\end{equation}

These parameters were chosen to provide a balanced response for steering control. The proportional gain ($K_p$) was set to 0.5 to ensure a moderate response to steering errors without causing excessive oscillations. The integral gain ($K_i$) was set to 0.0 to avoid accumulation of past errors, which is not critical for steering control in this context. The derivative gain ($K_d$) was set to 0.1 to provide damping and reduce overshoot, helping to smooth out the steering response.
